\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix typo

    \item[-] \textbf{Light client friendly:} The overwhelming majority of end users will need to securely access the platform in computing environments with resource cosntraints, such as browsers and mobile devices. They also should be able to quickly start interacting with the platform, even if the last sign-on was a long time ago, or it may even be the first time. In addition, the Joystream protocol will have a large state and transaction history. These constraints make a light client protocol the only genuine interaction model for almost all users.

>>>>

    \item[-] \textbf{Light client friendly:} The overwhelming majority of end users will need to securely access the platform in computing environments with resource constraints, such as browsers and mobile devices. They also should be able to quickly start interacting with the platform, even if the last sign-on was a long time ago, or it may even be the first time. In addition, the Joystream protocol will have a large state and transaction history. These constraints make a light client protocol the only genuine interaction model for almost all users.
